---
title: "Model Fitting"
author: "Applied Machine Learning with R<br/><a href='https://therbootcamp.github.io'>www.therbootcamp.com</a><br/><a href='https://twitter.com/therbootcamp'>@therbootcamp</a>"
date: "January 2019"
output:
  xaringan::moon_reader:
    css: ["default", "baselrbootcamp.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
---

layout: true

<div class="my-footer"><span>
<a href="https://therbootcamp.github.io/"><font color="#7E7E7E">Applied Machine Learning with R, January 2019</font></a>
&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;&emsp;
<a href="https://therbootcamp.github.io/"><font color="#7E7E7E">www.therbootcamp.com</font></a>
</span></div> 

---


```{r, eval = TRUE, echo = FALSE, warning=F,message=F}
# Code to knit slides
baselers <- readr::read_csv("../_data/baselers.csv")
```


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
# see: https://github.com/yihui/xaringan
# install.packages("xaringan")
# see: 
# https://github.com/yihui/xaringan/wiki
# https://github.com/gnab/remark/wiki/Markdown
options(width=110)
options(digits = 4)
```

```{r, echo = FALSE ,message = FALSE, warning = FALSE}
knitr::opts_chunk$set(comment=NA, fig.width=6, fig.height=6, echo = TRUE, eval = TRUE, 
                      message = FALSE, warning = FALSE, fig.align = 'center', dpi = 200)
library(tidyverse)
library(baselers)
library(ggthemes)
```


.pull-left4[

# What is a model?

]

.pull-right6[

]


---

.pull-left4[

# What models are there?

]

.pull-right6[

]

---

.pull-left4[

# What types of decision problems are there?

]

.pull-right6[

]

---


.pull-left4[

# What does it mean to 'fit' a model?

]

.pull-right6[

]


---


.pull-left4[

# 3 models

- Regression
- Tree Based
    - Decision Trees
    - Random Forests
- KNN

]

.pull-right6[

]


---

.pull-left4[

# Quantifying performance

Regression - Mean Squared error

]

.pull-right6[


]

---

.pull-left4[

# Quantifying performance

Classification

- Absolute classification error
- Balanced Accuracy
- AUC

]

.pull-right6[

]

---

# How do you know which features were important?

---
# Caret






---


# Practical

<font size=6><b><a href="https://therbootcamp.github.io/Intro2DataScience_2018Oct/_sessions/Plotting/Plotting_practical.html">Link to practical</a>






